### 2022-03-10 sections/introduction.tex
update most comments

%-------------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%-------------------------------------------------------------------------------
After the discovery of the Higgs boson in 2012 at the Large Hadron Collider (LHC) by the ATLAS~\cite{Aad:2012tfa} and 
CMS~\cite{Chatrchyan:2012ufa} collaborations, 
%Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
a comprehensive programme of measurements % of its properties
has been conducted to explore this new particle. Measurements so far proved to be consistent with the Standard Model (SM) predictions. 
However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standar Model (BSM)
are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 
the top quark, and an up-quark, $tqH$ ($q=u, c$), which has been actively searched for by the ATLAS and CMS collaborations.  
%with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
%for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
%However the LHC still provides an excellent opportunity to search for rare new physics processes beyond the Standard Model (BSM).  
%there are still chances to find new physics by improving the sensitivity of previous searches.
%The flavour-changing neutral-current (FCNC) interactions 
%between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations. %is still an active topic.
Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions could manifest themselves as FCNC top-quark decays~($t\to qH$)~\cite{Agashe:2013hma}.
%Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance 
%becomes non-zero, enhancing 
%the total
%production cross section of $pp\rightarrow tH$.

In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}. Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance
%becomes non-zero, enhancing
the total production cross section of $pp\rightarrow tH$.
The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small, $\BR(t\to qH)\approx10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}. 
%such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
%interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
%Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
%As a result, the SM predictions for the $t \to Hq$ branching 
%ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{Branco:2hdm2012} with or without flavour violation,
%of type I, with explicit flavour conservation,
%and of type II, such as
the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
%While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
%the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
%Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
%The $tqH$ interaction could also potentially open up more
%Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
%which could be interesting for future studies.
%Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through %this interaction would enhance 
%%becomes non-zero, enhancing 
%the total
%production cross section of $pp\rightarrow tH$.
The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at 13 TeV centre of mass energy~\cite{deFlorian:2016spz}.

@@

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{1}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
%& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The dataset is divided into several final states depending on the production mode and
the  $W$ decay. Top pair production events where the $W$ boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$ decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_{\ell}$). 
Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels. Events with at least one \tauhad with an additional electron or muon are named leptonic channels. More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
fake estimations from multi-jet background are implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

>>>>

%-------------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%-------------------------------------------------------------------------------
After the discovery of the Higgs boson in 2012 at the Large Hadron Collider (LHC) by the ATLAS~\cite{Aad:2012tfa} and 
CMS~\cite{Chatrchyan:2012ufa} collaborations, 
%Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
a comprehensive programme of measurements % of its properties
has been conducted to explore this new particle. Measurements so far proved to be consistent with the Standard Model (SM) predictions. 
However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standar Model (BSM)
are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 
the top quark, and an up-type quark, $tqH$ ($q=u, c$), which has been actively searched for by the ATLAS and CMS collaborations.  
%with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
%for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
%However the LHC still provides an excellent opportunity to search for rare new physics processes beyond the Standard Model (BSM).  
%there are still chances to find new physics by improving the sensitivity of previous searches.
%The flavour-changing neutral-current (FCNC) interactions 
%between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations. %is still an active topic.
Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions could manifest themselves as FCNC top-quark decays~($t\to qH$)~\cite{Agashe:2013hma}.
%Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance 
%becomes non-zero, enhancing 
%the total
%production cross section of $pp\rightarrow tH$.

In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}. Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance
%becomes non-zero, enhancing
the total production cross section of $pp\rightarrow tH$.
The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small, $\BR(t\to qH)\approx10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}. 
%such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
%interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
%Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
%As a result, the SM predictions for the $t \to Hq$ branching 
%ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
However, these branching ratios can as high as $\BR(t\to qH) \sim 10^{-5}$ which incorporate beyond the SM processes. Examples of these include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
 %of type I, with explicit flavour conservation,
 %and of type II, such as
the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial  compositeness~\cite{Azatov:2014lha}, 
or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
% In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
% Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ %Branco:2hdm2012} with or without flavour violation,
% %of type I, with explicit flavour conservation,
% %and of type II, such as
% the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
% supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial  %compositeness~\cite{Azatov:2014lha}, 
% or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
% In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation, since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
%While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
%the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
%Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
%The $tqH$ interaction could also potentially open up more
%Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
%which could be interesting for future studies.
%Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through %this interaction would enhance 
%%becomes non-zero, enhancing 
%the total
%production cross section of $pp\rightarrow tH$.
The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at centre-of-mass energies of $\sqrt{s}= 13~\tev$ centre of mass energy~\cite{deFlorian:2016spz}.

@@

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data. Each limit is obtained assuming the other branching ratio is 0}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{1}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The dataset is divided into several final states depending on the production mode and
the  $W$ decay. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$ decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_{\ell}$). 
Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels. Events with at least one \tauhad with an additional electron or muon are named leptonic channels. More signal regions (with top quark decay leptonically) are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
fake estimations from multi-jet background are implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

### 2022-03-10 sections/objects.tex
update most comments

Events are selected from $pp$ collisions at $\sqrt{s}$=13 TeV recorded by the ATLAS detector during 2015-2018.
Only events for which all relevant subsystems were operational are considered.
Events are required to have at least one vertex with two or more tracks with transverse momentum
%The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
%in neighbouring bunch crossings, referred to as pile-up. 
%Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks with transverse momentum
($\pt$) larger than $400~\mev$ that are consistent with originating from the 
beam collision region in the $x$--$y$ plane. If more than one primary vertex candidate is found, the
candidate whose associated tracks form the largest sum of squared $\pt$~\cite{ATL-PHYS-PUB-2015-026}
is selected as the hard-scatter primary vertex.

Electron candidates~\cite{ATLAS-CONF-2016-024,Aaboud:2018ugz} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight likelihood-based identification 
criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets.

Muon candidates~\cite{Aad:2016jkr} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are re-fitted using the complete track information from both detector systems.
Muon candidates are required to satisfy medium identification criteria~\cite{Aad:2016jkr}.

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5\,(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
%To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
direction of the electron (muon). The electron (muon) candidates ($\ell=e$ or $\mu$) are required to satisfy both
%$I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.

Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}. These additional reconstructed charged particle tracks inside the jet can be
used to increase the precision for identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
The tight working points are used for high $\pt$ lepton.
The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

>>>>

Events are selected from $pp$ collisions at $\sqrt{s}$=13 TeV recorded by the ATLAS detector during 2015-2018~\cite{DAPR-2018-01}.
Only events for which all relevant subsystems were operational are considered.
Events are required to have at least one primary vertex with two or more tracks with transverse momentum
%The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
%in neighbouring bunch crossings, referred to as pile-up. 
%Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks with transverse momentum
($\pt$) larger than $400~\mev$ that are consistent with originating from the 
beam collision region in the $x$--$y$ plane. If more than one primary vertex candidate is found, the
candidate whose associated tracks form the largest sum of squared $\pt$~\cite{ATL-PHYS-PUB-2015-026}
is selected as the hard-scatter primary vertex.

Electron candidates~\cite{EGAM-2018-01} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight likelihood-based identification 
criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets.

Muon candidates~\cite{MUON-2018-03} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are re-fitted using the complete track information from both detector systems.
Muon candidates are required to satisfy medium identification criteria~\cite{Aad:2016jkr}.

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5\,(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
%To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
direction of the electron (muon). The electron (muon) candidates are required to satisfy both
%$I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$ ($\ell=e$ or $\mu$).

Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}. These additional reconstructed charged particle tracks inside the jet can be
used to increase the accuracy for identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
The tight working points are used for high $\pt$ lepton.
The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
%Additionally, the $\Htautau$ search requires leptons to
%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
%percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.
